CDSR Human Data/Modelling Paper

### 2013-09-11 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
minor edits

\begin{abstract}
Representing and reasoning about spatial terms is an essential ability for cognitive systems interacting with humans in a shared environment.  Consider an agent asked to remain "in the safe zone" during a military engagement.  The size, shape, and location of this area depend on the capabilities of the agent, other agents in the scene, and the constraints imposed by the environment.  We call these types of regions \textit{context-dependent spatial regions}(CDSRs) due to the context-dependent nature of their extent.  We claim that understanding these regions requires integrating semantic and geometric knowledge about a dynamic environment as well as understanding how task-specific information influences spatial interpretation.  We report the results of a human study conducted to explore how people interpret three types of CDSRs and to support the knowledge integration claim.  We discss the implications for these results on cognitive systems development.
\end{abstract}

\section{Introduction - KLENK} 
Natural collaboration between humans and cognitive systems requires both participants to communicate using a shared understanding of spatial language.  Cognitive systems can do quite well with spatial terms defined in terms of coordinates on a map, or that can be specified using known landmarks.  However, many spatial terms are defined not only be their geometry, but also their context and their relevance to current goals.  That is, to understand this language requires considering the other objects and agents in the environment, as well as their configuration and functional roles.  We call such regions \textit{context-dependent spatial regions}(CDSRs).

We begin by discussing the features of CDSRs using illustrative examples.  We claim that (1) people can effectively communicate using these regions, and (2) the size and shape of these regions change with the context.  We argue that to account for this behavior, a cognitive systems solution must respond to changing context, apply learned regions to new situations, and reuse learned knowledge in multiple tasks.  To explore these claims, we present the results of a human study, in which, people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider a number of approaches from current cognitive systems and robotics.  Each approach has a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

\section{Context-Dependent Spatial Regions}
Consider the following regions (shown in Figure \ref{examples}): the front of a classroom , safety in military engagement, or the geographical feature of a bottleneck.  To identify these regions, one must identify the physical boundaries (e.g., walls, bodies of water), the objects within the environment, their orientation and their functional use (e.g., desks oriented toward a whiteboard), and other agents' intentions and capabilities (e.g., enemy tanks can move and have a range of attack).  Furthermore, these regions exist at different levels of spatial resolution.  Consider a neighborhood in a city, whose boundaries expand and contract overtime with changes to the surrounding residents and businesses.

@@

Understanding these regions is crucial to joint intelligent action with humans.  Not only are these regions frequently tied to goals and commands: "go to the front of the classroom", "defend the bottleneck", and "get to safety", but they are also central to understanding human activities: e.g., "Is there a class in session?".

The long-term goal of this work is to create intelligent agents that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new situations.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

@@

\subsection{Research Question, Design and Stimuli}

The study was designed to examine the following questions about CDSRs:
\begin{enumerate}
	\item Given a particular situation how well do people agree on the location and extent of a named context dependent spatial region?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given situation effect the location and extent of a named context dependent spatial region?
\end{enumerate}

Both of these research questions address the fundamental claim that CDSRs are contextually defines. Research question 1 addresses the contextual nature of CDSRs because if CDSRs are contextual dependent then one would expect a variation across the agreement between subjects for different context: in a context that afforded the use a particular CDSR one would expect to see a high agreement between subject reponses, conversely in a context where a CDSR was not appropriate one might expect little or no agreement between subjects. Research question 2 address the contextual nature of CDSRs. Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

To examine these questions, we developed two experimental tasks:
\begin{enumerate}
	\item Task 1: subjects were presented with a visual representation of a spatial scene and an linguistic description containing a CDSR and were tasked with drawing a polygon a polygon on the visual stimuli such that it defined the location and extent of the CDSR in the scene or to select a no region opt
	\item Task 2: subjects were presented with a visual representation of a spatial scene where a particular location in the scene had been marked and an accompanying spatial description and were taked with rating on a five point likert scale how well the marked location fitted with their understanding of the CDSR.
\end{enumerate}

Both Task 1 and 2 addressed both research questions. Between subject agreement metrics can be computed for both Task 1 and Task 2 and, consequently, both tasks address research question 1. In particular, a variation in between subject agreement across the different contexts for a particular CDSR could be taken as evidence that some contexts are more amenable to a particular CDSR than others and hence CDSRs are contextually dependent. By shifting the focus of the analysis to examining the variation in responses for a given CDSR in context that differed only with respect to the location of objects both the results from both tasks can address research question 2. In the case of Task 1 the variation we will examine is the area of the polygons, which in Task 2 the variation we will examine is the scoring of the marked locations.

We developed a set of visual stimuli depicting a human environment (such as a room floor plan or a map) each paired with an accompanying linguistic description of a CDSR easily understood within the context of that environment (such as \emph{go to the front of the room}).  Figure \ref{fig:exp_stimuli} presents the stimuli used in the experiment. These stimuli were used in both Task 1 and 2. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the domain and the spatial region that accompanied them: (1) the classroom domain stimuli were always accompanied by the spatial description \emph{the front of the classroom}; (2) the geographical map stimuli were always accompanied by the description \emph{the bottleneck}; and (3) the military engagement stimuli were always accompanied by the description \emph{safety}.

The classroom stimuli consisted of pairs of floor plans and photos of classrooms with different chair configurations. For example, Figure \ref{fig:classroom-a} is a floor plan of a classroom where the chairs have been arranged in a circle and Figure \ref{fig:classroom-b} is the accompanying photo of this classroom. We developed four different classroom stimuli each with a different layout of chairs: a circular chair layout, a U shaped layout (Figure \ref{fig:classroom-c} and Figure \ref{fig:classroom-d}), a typical row-based layout with the first row of chairs close to the expected front of the room (Figure \ref{fig:classroom-e}), and the same arrangement with the front row of chairs further away from the expected front of the room (Figure \ref{fig:classroom-f})\footnote{In the interest of saving space we do not show all the classroom photo stimuli}. To control for left-right bias effects two versions of the U shaped layout, close rows layout and far rows layout were created by horizontally flipping the layouts. Conseqeuntly, there were 7 classroom stimuli (circle, U $\times 2$, close $\times 2$, far $\times 2$). In designing these stimuli we deliberately chose some layouts that were very common or close variations on standard layouts - e.g., Figures \ref{fig:classroom-e} and \ref{fig:classroom-f} - and others were more novel - Figure \ref{fig:classroom-a} and \ref{fig:classroom-c}. By varying the typicality of the layouts we hoped to get some variation across the between subject agreement on a per stimuli basis, for example we expected to get a higher between subject agreement for the stimuli that were more common. This would provide insight into research question 1, in particular it would point to the effect of typicality on the semantics of contextually defined spatial regions. Also, because the typicality of the scenes was varied by adjusting the location and orientation of objects in the scenes, a variation in agreement across the stimuli would provide evidence that the orientation and location of objects do effect the location and extent of spatial regions.

@@

The geographical map stimuli, Figures \ref{fig:bottleneck-a} and \ref{fig:bottleneck-b}, differed in the width of the bottleneck region. We hoped this variation woudd result in a variation in the size of the polygons for these different visual contexts. Finally, the military engagement stimuli, Figures \ref{fig:tanks-a}, \ref{fig:tanks-b}, \ref{fig:turrets-a}, \ref{fig:tanks-b} varied the functionality of the objects in the scene (tanks that could move versus fixed turret emplacements), the location of the objects in the scenes (were the tanks close to the bottom of the image or near the top), and the number and layout of the objects (the number and layout of the turrets were varied). Again, a variation across the between subject agreement on the different stimuli would provide evidence for the impact of object location and orientation on spatial semantics.

@@

\subsection{Trial Type 1 - Design}
In the first set of trials, the subject was asked to draw a polygon that defined the extent of the CDSR given or to select a no region option.  The drawing was done on the diagram in all stimuli with the classroom photographs provided for reference in those trials.  Subjects drew polygons by clicking to position the verticies with lines being automatically generated between each point indicated as the subject drew.  There was no upper bound placed on the number of line segments drawn but subjects were required to provide at least three line segments or to choose no region before continuing to the next stimulus.

\subsection{Trial Type 1 - Results}
One well known metric for analysising interannotator agreement is the \textbf{Cohen's kappa coefficient}, $\kappa$. Cohen's kappa measures the agreement between two annotators who each classify a number of items into two or more mutually exclusive classes. $\kappa$ ranges from 0 indicating no agreement beyond chance to 1 indicating complete agreement. In order to use Cohen's kappa to measure the agreement between subject responses in our type 1 trials we generated a set of 47,000 test points that were uniformly distributed across each stimuli and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimuli basis. In this calculation if either of the subjects in a pair entered a no region response for a particular stimuli a $\kappa$ value of 0 was used. Figure \ref{fig:subj-kappa} shows a histogram of the per subject average kappa scores using ten equal width intervals covering the $\kappa$ range between 0 and 1.  It is evident from this figure that most subjects had a $\kappa$ score between $0.2-0.5$ with a overall majority of subjects having a $\kappa$ score between $0.3-0.4$. A $\kappa$ score between $0.3-0.4$ would be considered as being poor to fair. This would indicate that there was some agreement between subjects but less that would be expected. However, this calculation was done across all the stimuli and as we have already mentioned some of the stimuli were deliberately designed to be non-prototypical, in particular we expected the classroom stimuli where the chairs were arranged in a circle (Figure \ref{fig:classroom-a}) and in a U shaped pattern (Figure \ref{fig:classroom-c} and its horizontally flipped equivalent) to be relatively novel situations for the subjects. Indeed, if we look at the histogram of the average pairwise $\kappa$ scores by stimuli, Figure \ref{fig:stim-kappa}, it is evident that there is a large variation, ranging from $0$ to $0.8$, in $\kappa$ scores for each stimuli. In more detail, Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no regrion responses for each stimuli. It is clear from this table that the non-prototypical stimuli have the lowest $\kappa$ scores and also that there is relationship between typicality and the number of no region responses. Given this relatively large variation across stimuli, which we attribute to the prototypicality of the depicted situation, we computed the average pairwise $\kappa$ scores for each subject when the non-prototypical stimuli trials were excluded. Figure \ref{fig:subj-kappa-proto} presents the histogram of the resulting average pairwise subject  $\kappa$ scores by subject. Not surpringly, with the exclusion on the non-prototypical stimuli the average pairwise $\kappa$ scores increase, with over half the subjects having an average pairwise $\kappa$ score between $0.4$ and $0.6$. $\kappa$ scores in this range can to interpreted as fair to good.

@@

\subsection{Trial Type 2 - Design} 
In the second set of trials, a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region.  The location of these points was informed by the results of a pilot study and the final design of the study and they were positioned such that for each particular stimuli one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the described spatial region. In the classroom domain the three points were located along the horizontal line that bisected the stimuli with P1 positioned on the left of the stimuli, P2 in the center and P3 on the right of the stimuli (as shown in Figure \ref{fig:classroom-points}). One of the aims of this configuration of points was to provide comparable data points between the trials where the classroom stimuli were horizontally flipped. In the classroom domain the expected sweetspot varied between the points depending on the stimuli. In the map domain P1 was positioned in the top left corner of the stimuli,  P2 was the expected sweetspot and was located within the expected bottleneck region for both stimuli and P3 was located in the bottom right corner of the stimuli (see Figure \ref{fig:bottleneck-points}).  In the military engagement domain the three test points were located on the vertical line that bisected the stimuli: P1 was located near the top of the image in the proximity of the enemy tanks, P2 was located near the center of the image such that in some stimuli it was in a no-man's land position and in other stimuli (specifically stimuli (i) in the friendly tanks have moved forward and (l) where there is an extra friendly turret) it could be considered to be in a protected area, and P3 was located near the bottom of the stimuli and consequently was always located behind the friendly tanks/turrets. P3 was the expected sweetspot in the military engagement domain but it was also hoped that P2 rating would differ between the stimuli where it was in no-mans land and where it recieved some protection.

@@

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli using a confidence level of $95\%$. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli. Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the miliatary engagement domain between the pair of stimuli (i) and (j) and the pair of stimuli (k) and (l). In stimuli (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimuli (j) the P2 point is in no-mans land. Given this change in the context one would expect a higher ranking for the P2 point in context (i) than in context (j). As the results in Table \ref{tab:point-likert-scores} show this is the case with average rating of P2  stimuli (i) being higher than that for (j). This higher rating is statiscially significant at a $95\%$ confidence level. Stimuli (k) and (l) present and analagous situation with P2 being protected by an extra turret in stimuli (l) but in no-mans land in stimuli (k). Again, the average rating of P2 for stimuli (l) is higher than that of (k), although this difference is not statistically significant. Notice, that the rating of the sweetspot for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different sweetspots across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.

>>>>

\begin{abstract}
Representing and reasoning about spatial terms is an essential ability for cognitive systems interacting with humans in a shared environment.  Consider an agent asked to remain ``in the safe zone'' during a military engagement.  The size, shape, and location of this area depend on the capabilities of the agent, other agents in the scene, and the constraints imposed by the environment.  We call these types of regions \textit{context-dependent spatial regions}(CDSRs) due to the context-dependent nature of their extent.  We claim that understanding these regions requires integrating semantic and geometric knowledge about a dynamic environment as well as understanding how task-specific information influences spatial interpretation.  We report the results of a human study conducted to explore how people interpret three types of CDSRs and to support the knowledge integration claim.  We discss the implications for these results on cognitive systems development.
\end{abstract}

\section{Introduction} 
Natural collaboration between humans and cognitive systems requires both participants to communicate using a shared understanding of spatial language.  Cognitive systems can already understand spatial terms defined in terms of coordinates on a map~\cite{Zender2008a}, or that can be specified using known landmarks~\cite{brenneretal07ijcai}.  However, many spatial terms are defined not only by their geometry, but also their context and their relevance to current goals.  That is, to understand this language requires considering the other objects and agents in the environment, as well as their configuration and functional roles.  We call regions that can only be understood in this way \textit{context-dependent spatial regions} (CDSRs).

Section~\ref{sec:cdsrs} discusses the features of CDSRs using illustrative examples.  We claim that (1) people can effectively communicate using these regions, and (2) the size and shape of these regions change with the context.  We argue that to account for this behavior, a cognitive systems solution must respond to changing context, apply learned regions to new situations, and reuse learned knowledge in multiple tasks.  To explore these claims, we present the results of a human study, in which, people marked regions and rated points representing CDSRs in three different environments in 13 different contexts.  In discussing the results, we consider a number of approaches from current cognitive systems and robotics.  Each approach has a number of shortcomings that must be addressed not only to improve our understanding of human spatial reasoning, but also to enable robust intelligent assistants in human environments.

\section{Context-Dependent Spatial Regions}\label{sec:cdsrs}

Consider the following regions (shown in Figure \ref{fig:examples}): the front of a classroom, safety in a military engagement, or the geographical feature of a bottleneck.  To identify these regions, one must identify the physical boundaries (e.g., walls, bodies of water), the objects within the environment, their orientation and their functional use (e.g., desks oriented toward a whiteboard), and other agents' intentions and capabilities (e.g., enemy tanks can move and have a range of attack).  Furthermore, these regions exist at different levels of spatial resolution.  Consider a neighborhood in a city, whose boundaries expand and contract over time with changes to the surrounding residents and businesses.

@@

Understanding these regions is crucial to joint intelligent action with humans.  Not only are these regions frequently tied to goals and commands: ``go to the front of the classroom'', ``defend the bottleneck'', and ``get to safety'', but they are also central to understanding human activities: e.g., ``Is there a class in session?''.

The long-term goal of our work is to create cognitive systems that can naturally interact with people in human environments.  While the study presented below illustrates the importance of context, object types and configurations, on human spatial judgements, constructing a cognitive systems approach requires more than reproducing these results.  First, the representational approach should be transferable to new situations.  While humans do not demonstrate mastery after a single example of a concept, they are able to begin using it immediately refining it over time.  Second, the representation should be applicable in different reasoning tasks.  The functional nature of these regions makes them important for many tasks from action planning to activity recognition.

@@

\subsection{Research Questions, Design and Stimuli}

We developed the study described below in order to examine the following questions about CDSRs:
\begin{enumerate}
	\item Given a particular situation how well do people agree on the location and extent of a named CDSR?
	\item Does the orientation and location of objects (with relevant functional semantics) in a given situation effect the location and extent of a named CDSR?
\end{enumerate}

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Research question 1 addresses the contextual nature of CDSRs because if CDSRs are contextual dependent then one would expect a variation across the agreement between subjects for different context: in a context that afforded the use of a particular CDSR one would expect to see a high agreement between subject reponses, conversely in a context where a CDSR was not appropriate one might expect little or no agreement between subjects. Research question 2 address the contextual nature of CDSRs. Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

To examine these questions, we developed two experimental tasks:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli such that it defined the location and extent of the CDSR in the scene (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene where a particular location in the scene had been marked and an accompanying spatial description and were asked to rate how well the marked location fitted with their understanding of the CDSR on a five point likert scale.
\end{itemize}

Both Task 1 and 2 address both research questions. Between subject agreement metrics can be computed for both Task 1 and Task 2. In particular, a variation in between subject agreement across the different contexts for a particular CDSR could be taken as evidence that some contexts are more amenable to a particular CDSR than others and hence CDSRs are contextually dependent. By shifting the focus of the analysis to examining the variation in responses for a given CDSR in context that differed only with respect to the location of objects both the results from both tasks can address research question 2. In the case of Task 1 the variation we will examine is the area of the polygons, while in Task 2 the variation we will examine is the scoring of the marked locations.

We developed a set of visual stimuli depicting different environments, and paired each with an accompanying linguistic description of a CDSR easily understood within the context of that environment (see Figure \ref{fig:exp_stimuli}). These stimuli were used in both Task 1 and 2. Throughout the rest of the paper we will use the labels from Figure \ref{fig:exp_stimuli} as the names for the different stimuli. The stimuli can be broken into three groups based on the domain and the spatial region that accompanied them: (1) the classroom domain stimuli were always accompanied by the spatial description \emph{the front of the classroom}; (2) the military engagement stimuli were always accompanied by the description \emph{safety}; and (3) the geographical map stimuli were always accompanied by the description \emph{the bottleneck}.

The classroom stimuli consisted of pairs of floor plans and photos of classrooms with different chair configurations. For example, Figure \ref{fig:classroom-a} is a floor plan of a classroom where the chairs have been arranged in a circle and Figure \ref{fig:classroom-b} is the accompanying photo of this classroom. We developed four different classroom stimuli each with a different layout of chairs: a circular chair layout, a U shaped layout (Figure \ref{fig:classroom-c} and Figure \ref{fig:classroom-d}), a typical row-based layout with the first row of chairs close to the expected front of the room (Figure \ref{fig:classroom-e}), and the same arrangement with the front row of chairs further away from the expected front of the room (Figure \ref{fig:classroom-f})\footnote{In the interest of saving space we do not show all the classroom photo stimuli}. To control for left-right bias effects, two versions of the U shaped layout, close rows layout and far rows layout were created by horizontally flipping the layouts. Consequently, there were 7 classroom stimuli (circle, U $\times$ 2, close $\times$ 2, far $\times$ 2). In designing these stimuli we deliberately chose some layouts that were very common or close variations on standard layouts - e.g., Figures \ref{fig:classroom-e} and \ref{fig:classroom-f} - and others were more novel - Figure \ref{fig:classroom-a} and \ref{fig:classroom-c}. By varying the typicality of the layouts we hoped to get some variation across the between subject agreement on a per stimuli basis, for example we expected to get a higher between subject agreement for the stimuli that were more common. This would provide insight into research question 1, in particular it would point to the effect of typicality on the semantics of contextually defined spatial regions. Also, because the typicality of the scenes was varied by adjusting the location and orientation of objects in the scenes, a variation in agreement across the stimuli would provide evidence that the orientation and location of objects do effect the location and extent of spatial regions.

@@

The geographical map stimuli, Figures \ref{fig:bottleneck-a} and \ref{fig:bottleneck-b}, differed in the width of the bottleneck region. We hoped this variation would result in a variation in the size of the polygons for these different visual contexts. Finally, the military engagement stimuli, Figures \ref{fig:tanks-a}, \ref{fig:tanks-b}, \ref{fig:turrets-a}, \ref{fig:tanks-b} varied the functionality of the objects in the scene (tanks that could move versus fixed turret emplacements), the location of the objects in the scenes (were the tanks close to the bottom of the image or near the top), and the number and layout of the objects (the number and layout of the turrets were varied). Again, a variation across the between subject agreement on the different stimuli would provide evidence for the impact of object location and orientation on spatial semantics.

@@

\subsection{Trial Type 1 - Design}
In the first set of trials, the subject was asked to draw a polygon that defined the extent of the CDSR given or to select a no region option.  The drawing was done on the diagram in all stimuli with the classroom photographs provided for reference in those trials.  Subjects drew polygons by clicking to position the vertices with lines being automatically generated between each point indicated as the subject drew.  There was no upper bound placed on the number of line segments drawn but subjects were required to provide at least three line segments or to choose no region before continuing to the next stimulus.

\subsection{Trial Type 1 - Results}

One well known metric for analysising interannotator agreement is the \textbf{Cohen's kappa coefficient}, $\kappa$. Cohen's kappa measures the agreement between two annotators who each classify a number of items into two or more mutually exclusive classes. $\kappa$ ranges from 0 indicating no agreement beyond chance to 1 indicating complete agreement. In order to use Cohen's kappa to measure the agreement between subject responses in our type 1 trials we generated a set of 47,000 test points that were uniformly distributed across each stimuli and used each subject's polygon to classify the test points as being inside or outside the polygon. After classifying the test points for each subject we then computed an average pairwise kappa score for each subject with all the other subjects on a per stimuli basis. In this calculation if either of the subjects in a pair entered a no region response for a particular stimuli a $\kappa$ value of 0 was used. Figure \ref{fig:subj-kappa} shows a histogram of the per subject average kappa scores using ten equal width intervals covering the $\kappa$ range between 0 and 1.  It is evident from this figure that most subjects had a $\kappa$ score between $0.2-0.5$ with a overall majority of subjects having a $\kappa$ score between $0.3-0.4$. A $\kappa$ score between $0.3-0.4$ would be considered as indicating poor to fair agreement, i.e. there was some agreement between subjects but less that would be expected. However, this calculation was done across all the stimuli and as we have already mentioned some of the stimuli were deliberately designed to be non-prototypical, in particular we expected the classroom stimuli where the chairs were arranged in a circle (Figure \ref{fig:classroom-a}) and in a U shaped pattern (Figure \ref{fig:classroom-c} and its horizontally flipped equivalent) to be relatively novel situations for the subjects. Indeed, if we look at the histogram of the average pairwise $\kappa$ scores by stimuli, Figure \ref{fig:stim-kappa}, it is evident that there is a large variation, ranging from $0$ to $0.8$, in $\kappa$ scores for each stimuli.

In more detail, Table \ref{tab:stimuli-kappa-scores} lists the average pairwise $\kappa$ score for each of the visual stimuli used in the experiment and the number of no region responses for each stimuli. It is clear from this table that the non-prototypical stimuli have the lowest $\kappa$ scores and also that there is relationship between typicality and the number of no region responses. Given this relatively large variation across stimuli, which we attribute to the prototypicality of the depicted situation, we computed the average pairwise $\kappa$ scores for each subject when the non-prototypical stimuli trials were excluded. Figure \ref{fig:subj-kappa-proto} presents the histogram of the resulting average pairwise subject  $\kappa$ scores by subject. Not surpringly, with the exclusion on the non-prototypical stimuli the average pairwise $\kappa$ scores increase, with over half the subjects having an average pairwise $\kappa$ score between $0.4$ and $0.6$. $\kappa$ scores in this range can be interpreted as fair to good.

@@

\subsection{Trial Type 2 - Design} 
In the second set of trials, a location was marked on the visual stimuli (using a red dot) and the subject was asked to rank on a five point likert scale their judgement of how well the location matched the described spatial region.  The location of these points was informed by the results of a pilot study. In the final study they were positioned such that one of the domain's points, called the \textbf{sweetspot}, was located near the expected prototypical center of the described spatial region. In the classroom domain the three points were located along the horizontal line that bisected the stimuli with P1 positioned on the left of the stimuli, P2 in the center and P3 on the right of the stimuli (as shown in Figure \ref{fig:classroom-points}). One of the aims of this configuration of points was to provide comparable data points between the trials where the classroom stimuli were horizontally flipped. In the classroom domain the expected sweetspot varied between the points depending on the stimuli. In the map domain P1 was positioned in the top left corner of the stimuli,  P2 was the expected sweetspot and was located within the expected bottleneck region for both stimuli and P3 was located in the bottom right corner of the stimuli (see Figure \ref{fig:bottleneck-points}).  In the military engagement domain the three test points were located on the vertical line that bisected the stimuli: P1 was located near the top of the image in the proximity of the enemy tanks, P2 was located near the center of the image such that in some stimuli it was in a no-man's land position and in other stimuli (specifically stimuli (i) in the friendly tanks have moved forward and (l) where there is an extra friendly turret) it could be considered to be in a protected area, and P3 was located near the bottom of the stimuli and consequently was always located behind the friendly tanks/turrets. P3 was the expected sweetspot in the military engagement domain but it was also hoped that P2 rating would differ between the stimuli where it was in no-mans land and where it recieved some protection.

@@

As noted above, we controlled for left-right bias by flipping some of the stimuli on the horizontal axis. These flipped stimuli included the classroom stimuli (c), (e) and (f). This flipping of stimuli gave us the opportunity to compare the results of the sweetspots rankings between this pairs of stimuli trials. Given the horizontal flipping of the stimuli it was expected that the sweetspot for the stimuli should also be flipped between P1 and P3. To test whether or not the expected shift in the sweetspots occurred we ran two-tailed two sample t-tests between the sweetspots of the flipped and non-flipped stimuli pairs. In all cases the results indicated that there was no statistical difference between the rating of the sweetspot for the non-flipped stimuli and the rating of the sweetspot for the flipped stimuli using a confidence level of $95\%$. In other words, the sweetspot flipped from P1 to P3 systematically with the horizontal flipping of the stimuli.

Another way of testing the relationship between the variation in context and the variation in definition of the CDSRs is to look at the differences in the ranking of the P2 point in the miliatary engagement domain between the pair of stimuli (i) and (j) and the pair of stimuli (k) and (l). In stimuli (i) the friendly tanks are positioned between the P2 point and the enemy tanks whereas in stimuli (j) the P2 point is in no-mans land. Given this change in the context one would expect a higher ranking for the P2 point in context (i) than in context (j). As the results in Table \ref{tab:point-likert-scores} show this is the case with average rating of P2  stimuli (i) being higher than that for (j). This higher rating is statiscially significant at a $95\%$ confidence level. Stimuli (k) and (l) present and analagous situation with P2 being protected by an extra turret in stimuli (l) but in no-mans land in stimuli (k). Again, the average rating of P2 for stimuli (l) is higher than that of (k), although this difference is not statistically significant. Notice, that the rating of the sweetspot for the stimuli (i) and (l) remain quite high. This would indicate that the increase in the rating of the P2 points for these stimuli results from an increase in the area of the CDSR rather than a moving of the locus of the CDSR. Overall, the analysis of the ratings of the different sweetspots across the non-flipped and flipped stimuli and the variation in the ratings of the P2 points in the military domain stimuli point to the fact that both the location and the extent of a CDSR is contextually dependent.
